Perturbed Gait Data

### 2014-11-15 paper.tex
added source code and pdf images
simulink diagram removed

The resulting output from the MATLAB script and Simulink produces a comma-
delimited text file of six columns: timestamp, slow, normal, and fast walking
perturbation signals, and slow and fast running signals.  These running signals
were generated in the event the testing protocol expanded from a walking study
to a running study, though they were not used in the data set.

>>>>

The resulting output from the MATLAB script and Simulink produces a comma-
delimited text file of six columns: timestamp, slow, normal, and fast walking
perturbation signals, and slow and fast running signals.  These running signals
were generated in the event the testing protocol expanded from a walking study
to a running study, though they were not used in the data set.  The actual motion
of the treadmill belts are compared to the original input signals is shown in 
Figure~\ref{fig:input_output}.   The standard deviations of the outputs were 
calculated at 6.07\%, 9.68\%, and 12.68\% for the the 0.8, 1.2, and 
1.6 $m \cdot s^{-1}$ speeds, respectively.

\begin{figure}
  \includegraphics{figures/input_vs_output.pdf}
  \caption{Generated input signal (black) and actual treadmill belt movement
                (red) for average speeds of 0.8, 1.2, and 1.6 m/s, respectively}
  \label{fig:input_output}
\end{figure}

For further analysis, the input and output signals were transformed into the 
frequency domain through the Fast Fourier algorithm, and the results are
shown in Figure~\ref{fig:freq_analysis}.  It was observed that for the 1.2 $m \cdot s^{-1}$
average walking speed, the amplitude of the output is significantly lower 
than the amplitude of the input signal at lower frequencies.  Additionally, the 
amplitude of output signal in the 0.8 $m \cdot s^{-1}$ walking speed begins to attenuate 
around 2 Hz, which is a noticeably lower frequency than the other walking 
speeds.

\begin{figure}
  \includegraphics{figures/frequency_analysis.pdf}
  \caption{Frequency analysis of the  input (black) and output (red)
                for average speeds of 0.8, 1.2, and 1.6 m/s, respectively}
  \label{fig:freq_analysis}
\end{figure}
